---
title: "Python Setup in R with Reticulate"
author: "Aditya Mathur"
date: "25/04/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE
)
```
# Step 1 - Reticulate Setup
Fire up an R Markdown document and load tidyverse and reticulate:

1. tidyverse - Loads the core data wrangling and visualization packages needed to work in R.
2. reticulate - The key link between R and Python.

```{r}
library(tidyverse)
library(reticulate)

```
#Step 2 - Conda Installation
Next, we need to make sure we have the Python Environment setup that we want to use. For Python Environments, we will use Anaconda (Conda), a python environment management tool specifically developed for data scientists.

Download Conda

* Anaconda Distribution - [Installation Instructions](https://docs.anaconda.com/anaconda/install/)
Create a New Python Environment

Run the following code in your terminal:

conda create -n py3.8 python=3.8 scikit-learn pandas numpy matplotlib

his code does the following:

1. Creates a new Python environment called “py3.8”
2. Installs python version 3.8
3. Installs the latest versions of scikit-learn, pandas, numpy, and matplotlib.
In the future you can always add more python packages (you can toggle between environments using conda activate and conda deactivate commands)

Conda Terminal Commands
At some point you will need to create, modify, add more packages to your Conda Environment(s). Here are 4 useful commands:

Run conda env list to list the available conda environments
Run conda activate <env_name> to activate a conda environment
Run conda update --all to update all python packages in a conda environment.
Run conda install <package_name> to install a new package

List your Conda Environments (in the Terminal)
Use conda list env to list your Conda Environments in the Terminal.
If you see py3.8, you are good to go.

# List your Conda Enviromnents (in R Markdown)
Back in R Markdown, we can do the same thing using retculate::conda_list()

```{r}
reticulate::conda_list()
```
Set Your Conda Environment (in R Markdown)
Make sure your R Markdown document activates the “py3.8” environment using use_condaenv().
```{r}
# Replace this with your conda environment containing sklearn, pandas, & numpy
use_condaenv("py3.8", required = TRUE)
```
Double check that reticulate is actually using your new conda env.

```{r}
reticulate::py_config()
```

